Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-09-22 paper/main.tex
filled in description of regression-based prediction analyses

\subsubsection*{Regression-based prediction analyses}

>>>>

\subsubsection*{Regression-based prediction analyses}
Following our exploratory correlation analyses, we used an analogous
bootstrap procedure to identify subsets of memory-related,
fitness-related, and demographic-related variables that predicted
(non-overlapping) subsets of other variables.  For example, we tested
whether a combination of fitness-related variables could predict a
combination of memory-related variables, and so on.

We used the same bootstrap procedure described above (used in our
exploratory correlation analyses) to generate $N = 1000$ bootstrapped
data matrices whose rows reflected sampled participants and whose
columns reflected different measured variables.

We grouped variables according to whether they were memory-related,
fitness-related, or demographic-related.  For each bootstrap
iteration, we divided the rows of that iterations data matrix into
training and test sets.  The assignments of rows to these two sets was
random, subject to the constraint that any duplicated rows in the data
matrix (i.e., reflecting a single participant who had been sampled
multiple times) was always assigned to either the training \textit{or}
the test set--i.e., duplicated rows could not appear in both the
training and the test sets.  The training sets always comprised 75\%
of the data, and the tests sets comprised the remaining 25\% of the
data.

Next, we fit a series of ridge regression models to the training
data.  Specifically, for each pairing of memory, fitness, and
demographic variables, we fit a single ridge regression model treating
the first variable group as the input features and the second variable
group as the target features.  For example, one regression model used
memory variables to predict fitness variables, and another regression
model used fitness variables to predict demographic variables, and so
on.  In total we fit six regression models to each training dataset.
We then applied the fitted models to the held-out test dataset and
computed the root mean squared deviation (RMSD) between the predicted and
observed values in the target features of the test dataset.  We also
examined the regression weights assigned to each input feature.  This
yielded, for each regression model (across $N$ bootstrap iterations) a
distribution of RMSD values and a distribution of weights for each
input variable.

We constructed a ``null'' distribution by using the same procedure as above,
but where the columns in the test datasets were randomly permuted with
each iteration (thereby breaking any meaningful predictive information
between the training and test data).  We assessed the statistical
significance ($p$-values) of the observed RMSD values by computing the proportions
of null RMSD values that were less than the observed value.  We also
assessed the significance of the observed regression weights using
$t$-tests to compare the means of the observed versus null
distributions of weights.
